---
title: "Information choice and economic complexity"
subtitle: ""
author: "Cameron Pfiffer"
institute: "University of Oregon"
date: "October 1st, 2021"
output:
  beamer_presentation:
    keep_tex: yes
  ioslides_presentation:
    css: tufte-css-gh-pages/tufte.css
header-includes:
 - \usepackage{/home/cameron/Dropbox/Presentations/cbeamer/cstyle}
 - \usepackage{booktabs}
 - \usepackage{graphicx}
 - \usepackage[labelformat=empty]{caption}
 - \usepackage{dcolumn}
 - \usepackage{anyfontsize}
 - \usepackage{adjustbox}
 - \usepackage[T1]{fontenc}
 - \usepackage{relsize}
 - \usepackage{bm}
 - \usepackage{physics}
 - \usepackage{booktabs}
 - \usepackage{longtable}
 - \usepackage{array}
 - \usepackage{multirow}
 - \usepackage{wrapfig}
 - \usepackage{float}
 - \usepackage{colortbl}
 - \usepackage{pdflscape}
 - \usepackage{tabu}
 - \usepackage{threeparttable}
 - \usepackage{threeparttablex}
 - \usepackage[normalem]{ulem}
 - \usepackage{makecell}
 - \usepackage{xcolor}
 - \usepackage{hhline}
 - \usepackage{adjustbox}
 - \usepackage{soul}
# bibliography: ../references.bib
# csl: ../journal-of-finance.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)
# library(ggplot2)
# library(tidyverse)
# library(lubridate)
# library(ggthemes)
# library(strucchange)
# library(xts)
```

```{r fig.align='center',  out.width='0.9\\paperheight'}
# magick::image_transparent(magick::image_read("table8.png"), 'white', fuzz = 0)
```

# Research question

## Research question

How should you choose what information to analyze when the economy is ex-ante complicated?

Alternatively, how much information is it \blue{rational to ignore}?

## Information choice

\red{Information choice} is the study of how investors choose what things they wish to know about.

In asset pricing, we like to think about how information choice impacts things like

- Expected returns
- Risk premia
- Welfare (?)

I use "information choice" and "attention" synonymously.

## My hypothesis

I am trying to find out whether "complex" economies cause the basic findings of information choice models to fall apart.

Common findings:

- When a "common component" of payoffs or returns becomes more volatile, more attention goes to the common component. Common component here might be the business cycle or market returns.
- Increased attention reduces excess volatility, while decreased attention increases excess volatility.
- Prices are informative about payoffs because prices are a function of investor attention.

## Hypothesis 1

Investors allocate attention in a way that can systematically mislead them about the state of the economy.

## Hypothesis 2

Attention allocation can increase or decrease excess volatility/returns in a biased way.

## Hypothesis 3

Prices may be \red{very informative} or \blue{not informative at all}, since investors with different information can interperet prices radically differently.

## My hypothesis

In short -- the \textbf{findings of information choice models might not be as clear in complex economies}!

## Brief literature review

- Theory
  - Kacperczyk et al. (2016) is the model I follow closest, though I do away with a lot of their simplifying assumptions.
  - Peng and Xiong (2006) looks at category learning and attention.
  - Slow learning and model ambiguity can explain all kinds of variance phenomena (Ghaderi et al., 2021)
- Empirics
  - Kholhas and Walther (2021) asymmetric attention to procyclical variables can explain underreaction + extrapolation.
  - Cziraki et al. (2021) local/nonlocal bias in attention allocation causes abnormalities in returns.
  - Hirshleifer and Sheng (2021) shows that macro news triggers higher attention in firm-level securities.

# Complexity

## Complexity

```{r fig.align='center',  out.width='0.9\\paperheight'}
magick::image_transparent(magick::image_read("../plots/params/baseline/prior.png"), 'white', fuzz = 0)
```

Traditional models of information choice use unimodal joint densities with good properties. The above is the case used in Kacperczyk et al. (2016).

## Complexity

```{r fig.align='center',  out.width='0.9\\paperheight'}
magick::image_transparent(magick::image_read("../plots/params/baseline/prior.png"), 'white', fuzz = 0)
```

Gaussian variables are highly compact in any dimension, in that they are "spherical". They have an extremely small isoperimetric inequality (you can put a dense small "circle" around them).

## Complexity

The simplicity of the Gaussian distribution can cause a _signal_ about a payoff to be easily inferred.